\setuppapersize[A4][A4]      % Velikost papíru bude A5 a bude na stránce opět o téže velikosti. 
\setupcolors[state=start]    % Zapne používání barev.
\setuppagenumbering[state=stop]
\setuplayout[width=middle, topspace=1cm, header=1cm, footer=1cm]

\usemodule[handlecsv]
\setheader

\setupbodyfont[cmr,sansserif,10pt]

\setupwhitespace[medium]

\input lib-lua



\unexpanded\def\lineaction{
		%\vodoznakGyZA
		\hlavicka
		\hrule
		\blank[big]
		
		\adresnistitek{\CjPozvanka }{31.3.2010}
		
			\blank[10mm]

			{\tfa Invitation to entrance examination}
				
			\blank[big]	
			
			Madam,\crlf
			sir,
			
			\blank[big]	
			
			the filing of a secondary school was opened administrative proceedings regarding the admission of applicants
			  
			
			
			\blank[big]
			
			\uchazec
						
			\blank[big]
								
			
education in secondary school, whose work is carried out Gymnasium, Zábřeh, Liberation Square 20, in the field of  79-41-K/81 Gymnasium.

The admission procedure will be followed in accordance with the ~ ~ criteria for admission procedure ref 3/2010 established by the school head. 


In accordance with the criteria for the admission procedure will be included 
in the admission procedure entrance exam, which will include a test of general 
study prerequisites supplied by www.scio.cz, Ltd. {\bf The entrance exam} will 
be held on {\bf \TerminPZ} from 7:45 pm in the Grammar School, Zábřeh, 
Liberation Square 20.

When evaluating a publication of the results of the admission procedure, candidates will
labeled registration numbers. The registration number will be allocated to applicants
during the briefing before the start of the entrance exams. Results admission
the proceedings will be posted on the bulletin board in the lobby of the school and on the Internet ~
school site {\bf www.ourhighschool.cz}.

{\bf Please read the enclosed information carefully!}
 
{\bf Bring a thin black marker thickness of 0.3!}

{\bf No other aids are not candidates for the exam need!}

			
			\blank[3*big]
			
			\podpisreditele

\page
} 


\starttext
\setheader
\filelineaction{8l.csv}
\filelineaction{4l.csv}
\filelineaction{4l-n.csv}


\stoptext
	
